My title

### 2024-11-16 paper/paper.qmd
data/response variable

library(tidyverse)
library(palmerpenguins)

@@

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false
```

>>>>

library(tidyverse)

@@

## Overview Check packages

For this analysis, we combined four data sets all together into one. All these four data sets comes from **Worldbank** open data platform (@worldbank). We employed **R** (@citeR), a coding platform to download, clean and conduct statistical analysis. Besides, we also utilized R packages **tidyverse** (@tidy), **rstanarm** (@rstanarm), **ggplot2** (@gg), **knitr** (@knitr), **arrow** (@arrow), **here** (@here), and **dpylr** (@dplyr). The paper is outlined in github using starter folder provided in **Telling Stories With Data** (@tellingstories).

@@

The response variable in our analysis is the mortality rate below 5 year-old children for all countries. Here Mortality rate is calculated based on number of deaths of children under 5 years old per 1000 person. The histogram of this variable is shown in @fig-mor-1. We observe that the data ranges from 0 to 120, with a peak at 10-15.

However, this data is extremely right skewed and have several outlyers, thus we decided to perform log transformation to stabilize the variance and in-proving the normality of our dataset for a better regression model latter. The distribution after we perform log transformation is shown in @fig-mor-2, here the distribution is approximately normal ranging from 2 to 5 with a peak at 3.

```{r}
#| label: fig-mor
#| fig-cap: Histogram for Mortality rate of different countries
#| fig-subcap: ["Dsitribution before log tranformation", "Distribution after log transformation"]
#| echo: false
#| warning: false
#| message: false

# Load necessary libraries
library(ggplot2)
library(arrow)

# Read the data
data <- read.csv(file = (here::here('data/01-raw_data/raw_data_Mortality.csv')))

# Create the histogram
ggplot(data, aes(x = SH.DYN.MORT)) +
  geom_histogram(binwidth = 10, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Under-Five Mortality Rate",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 10)
  )

analysis_data <- read_parquet(file = (here::here('data/02-analysis_data/analysis_data.parquet')))

# Create the histogram
ggplot(analysis_data, aes(x = Mortality)) +
  geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Under-Five Mortality Rate",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 10)
  )

@@
